\documentclass[11pt]{article}

% NOTE: The "Edit" sections are changed for each assignment

% Edit these commands for each assignment

\newcommand{\assignmentduedate}{March 16}
\newcommand{\assignmentassignedate}{March 7}
\newcommand{\assignmentnumber}{One}

\newcommand{\labyear}{2018}
\newcommand{\assignedday}{Wednesday}
\newcommand{\dueday}{Friday}
\newcommand{\labtime}{9:00 am}

\newcommand{\assigneddate}{Announced: \assignedday, \assignmentassignedate, \labyear{} at \labtime{}}
\newcommand{\duedate}{Quiz: \dueday, \assignmentduedate, \labyear{} at \labtime{}}

% Edit this commands to describe key deliverables

\newcommand{\reflection}{\lstinline{writing/reflection.md}}

% Commands to describe key development tasks

% --> Running gatorgrader.sh
\newcommand{\gatorgraderstart}{\command{./gatorgrader.sh --start}}
\newcommand{\gatorgradercheck}{\command{./gatorgrader.sh --check}}

% --> Compiling and running program with gradle
\newcommand{\gradlebuild}{\command{gradle build}}
\newcommand{\gradlerun}{\command{gradle run}}

% Commands to describe key git tasks

% NOTE: Could be improved, problems due to nesting

\newcommand{\gitcommitfile}[1]{\command{git commit #1}}
\newcommand{\gitaddfile}[1]{\command{git add #1}}

\newcommand{\gitadd}{\command{git add}}
\newcommand{\gitcommit}{\command{git commit}}
\newcommand{\gitpush}{\command{git push}}
\newcommand{\gitpull}{\command{git pull}}

\newcommand{\gitcommitmainprogram}{\command{git commit src/main/java/labone/DisplayOutput.java -m "Your
descriptive commit message"}}

% Use this when displaying a new command

\newcommand{\command}[1]{``\lstinline{#1}''}
\newcommand{\program}[1]{\lstinline{#1}}
\newcommand{\url}[1]{\lstinline{#1}}
\newcommand{\channel}[1]{\lstinline{#1}}
\newcommand{\option}[1]{``{#1}''}
\newcommand{\step}[1]{``{#1}''}

\usepackage{pifont}
\newcommand{\checkmark}{\ding{51}}
\newcommand{\naughtmark}{\ding{55}}

\usepackage{listings}
\lstset{
  basicstyle=\small\ttfamily,
  columns=flexible,
  breaklines=true
}

\usepackage{fancyhdr}

\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}

\pagestyle{fancy}

\fancyhf{}
\rhead{Computer Science 103}
\lhead{Quiz \assignmentnumber{}}
\rfoot{Page \thepage}
\lfoot{\duedate}

\usepackage{titlesec}
\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

\newcommand{\guidetitle}[1]
{
  \begin{center}
    \begin{center}
      \bf
      CMPSC 103\\Introduction to Web Development\\
      Spring 2018\\
      \medskip
    \end{center}
    \bf
    #1
  \end{center}
}

\begin{document}

\thispagestyle{empty}

\guidetitle{Quiz \assignmentnumber{} Study Guide \\ \assigneddate{} \\ \duedate{}}

\section*{Introduction}

\noindent
The quiz will be ``closed notes'' and ``closed book'' and it will cover the
following materials. Please review the ``Course Schedule'' on the Web site for
the course to see the content and slides that we have covered to this date.
Students may post questions about this material to our Slack team.

\begin{itemize}

  \itemsep 0in

  \item Chapters One through Five in FWD, all sections (see online schedule for
    complete details).

  \item Using the commands in the terminal window (e.g., \program{cd} and
    \program{ls}); creating and viewing web sites with Markdown, HTML, and CSS;
    knowledge of the commands for using \program{git} and GitHub.

  \item All of your class notes and the discussion slides available from the
    course web site.

  \item Source code and writing for laboratory assignments 1--7 and practical
    assignments 1--6.

\end{itemize}

\noindent The quiz will be a mix of questions that have a form such as fill in
the blank, short answer, true/false, and completion. The emphasis will be on the
following topics:

\vspace*{-.05in}
\begin{itemize}

  \itemsep 0in

  \item Concepts in web development and the HTML and CSS languages (e.g., key
    definitions).

  \item Practical laboratory techniques (e.g., creating, debugging, and viewing
    web sites; effectively using files and directories; correctly using GitHub
    through the command-line {\tt git} program).

  \item Understanding Web sites (e.g., given a short, perhaps even one line,
    source code segment written in Markdown, HTML, and/or CSS, understand what
    it does and be able to precisely describe its resulting output as evident in
    the web server logs or in the web browser).

  \item Programming Markdown, HTML, and/or CSS statements in a web site, given a
    description of a site's appearance and behavior. Students should be
    completely comfortable with writing short source code statements that are in
    a nearly correct form. While your web site may contain small syntactic
    errors, it is not acceptable to ``make up'' features of the Markdown, HTML,
    and CSS programming language that do not currently exist. Given a source
    code segment you should also be able to sketch what a web site would look
    like in a web browser.

\end{itemize}

\noindent No partial credit will be given for questions that are true/false,
completion, or fill in the blank. Minimal partial credit may be awarded for the
questions that require a student to write a short answer. You are strongly
encouraged to write short, precise, and correct responses to all of the
questions. When you are taking the quiz, you should do so as a ``point
maximizer'' who first responds to the questions that you are most likely to
answer correctly for full points. Please keep the time limitation in mind as you
are absolutely required to submit the examination at the end of the class period
unless you have written permission for extra time from a member of the Learning
Commons. Students who do not submit their quiz on time will have their overall
point total reduced. Finally, students may only reschedule the quiz for a
different date or time if they are facing documented extenuating circumstances
that prevent them from attending the scheduled time slot. Please see the course
instructor if you have questions about any of these policies.

\section*{Reminder Concerning the Honor Code}

\noindent Students are required to fully adhere to the Honor Code during the
completion of this quiz. More details about the Allegheny College Honor Code are
provided on the syllabus. Students are strongly encouraged to carefully review
the full statement of the Honor Code before taking this quiz. If you do not
understand Allegheny College's Honor Code, then please schedule a meeting with
the course instructor. The following is a review of the Honor Code statement
from the course syllabus:

\begin{quote}
The Academic Honor Program that governs the entire academic program at
Allegheny College is described in the Allegheny Academic Bulletin. The Honor
Program applies to all work that is submitted for academic credit or to meet
non-credit requirements for graduation at Allegheny College. This includes all
work assigned for this class (e.g., examinations, laboratory assignments, and
the final project). All students who have enrolled in the College will work
under the Honor Program. Each student who has matriculated at the College has
acknowledged the following pledge:
\end{quote}

\vspace*{-.15in}

\begin{quote}
  I hereby recognize and pledge to fulfill my responsibilities, as defined in
  the Honor Code, and to maintain the integrity of both myself and the College
  community as a whole.
\end{quote}

\section*{Detailed Review of Content}

The listing of topics in the following subsections is not exhaustive; rather,
it serves to illustrate the types of concepts that students should study as
they prepare for the quiz. Please see the course instructor during office hours
if you have questions about any of the content listed in this section.

\vspace*{-.15in}

\subsection*{Chapter One}

\begin{itemize}

  \itemsep 0in

  \item The similarities and differences between an intranet and the Internet
  \item The similarities and differences between static and dynamic web sites
  \item An understanding of the client-server model and the ``request-response''
    loop
  \item How networks, routers, and Internet service providers enable a
    connection to a web site
  \item The different roles and skills associated with the field of web development
  \item A high-level understanding of the technologies used to create web sites
  \item The role that a version control system plays in the development of a web
    site

\end{itemize}

\vspace*{-.2in}
\subsection*{Chapter Two}

\begin{itemize}

  \itemsep 0in

  \item An intuitive understanding of the Internet protocols supporting a
    connection to a web site
  \item How the Domain Name System supports the registration of and the access
    to a web site
  \item The meaning, purpose, and structure of a uniform resource locator for a
    web site
  \item The role that web server ports play in furnishing access to a web site
  \item Details concerning the hypertext transfer protocol (HTTP) and its
    common response codes
  \item A detailed understanding of the steps that a browser takes to parse HTML
    and handle requests
  \item Knowledge of the web server's activities and the terminal-based output
    of a web server
  \item The motivation for and ways in which both web browsers and servers employ
    caching
  \item A basic understanding of the various ``application stacks'' employed
    by different web servers

\end{itemize}

\vspace*{-.2in}
\subsection*{Chapter Three}

\begin{itemize}

  \itemsep 0in

  \item The term ``markup language'' and a historical understand of the
    hypertext markup language
  \item An understanding of the web-related terms ``tag'', ``markup'', ``data'',
    and ``meta data''
  \item Knowledge of the terms ``syntax'' and ``semantics'' and how they
    connect to web development
  \item Familiarity with the canonical structure of an HTML file that
    uses cascading style sheets
  \item An understanding of commonly used tags in an HTML file (e.g., \program{<head>},
    \program{<p>}, and \program{<div>})
  \item Given the directory tree for a web site, the ability to explain
    different relative references
  \item Strategies for include accessible images and international character
    entities in web sites
  \item The benefits associated with using semantic markup in the fifth version
    of the HTML
  \item How to appropriately use tools to support the development and
    debugging of web sites

\end{itemize}

\vspace*{-.2in}
\subsection*{Chapter Four}

\begin{itemize}

  \itemsep 0in

  \item The benefits of using cascading style sheets to style a web site
  \item The relationship between the CSS and the HTML source code in a web site
  \item The syntax and semantics of source code for declaring and applying CSS
    styles
  \item Knowledge of common CSS properties and the way in which they influence
    a page's display
  \item The rules that govern how CSS styles interact (e.g., inheritance,
    specificity, and location)
  \item The CSS box model and the use of margins and padding to influence a web
    page's formatting
  \item The way to use the ``TRBL'' shortcut to remind you how to control the
    borders of elements
  \item The ways to install, configure, and style fonts downloaded from Google's
    font archive
  \item An understanding of font sizes and the units of measurement used to
    specify their size
  \item How to appropriately use tools to support the development and
    debugging of CSS files

\end{itemize}

\vspace*{-.2in}
\subsection*{Chapter Five}

\begin{itemize}

  \itemsep 0in

  \item The way in which HTML tables support the organization of data into rows
    and columns
  \item The meaning and behavior of the HTML tags supporting the creation of 
    tables
  \item The similarities and differences between table headers, rows, and data
    elements
  \item The benefits and drawbacks associated with using tables for web page
    layout
  \item How to style HTML tables with CSS that changes, for instance, table
    borders and backgrounds
  \item An understanding of the CSS source code needed to create tables that
    have a ``zebra effect''
  \item The way to create interactive tables through the use of CSS-based
    properties for hovering
  \item The meaning and behavior of the HTML tags needed to create a form in a
    web page
  \item The similarities and differences in the appearance and behavior of form
    control elements
  \item Strategies for supporting forms in a static web site that does not have
    access to a database
  \item The challenges associated with creating date and time controls in a web
    page's form
  \item The motivation for and benefits of creating tables and forms that
    support accessibility
  \item How to appropriately use tools to support the development and
    debugging of tables and forms

\end{itemize}

\end{document}
